On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2018-07-23 docs/mvfits_paper/mvf.tex
completing gmvr topy problem section ... for now

Under this perspective we will consider test data generated with the following parameters:
$\mu = 50.0$,
$a_0 = 1.1$,
$a_1 = 0.2$,
$a_2 = 0.5$,
$a_3 = 1.0$,
$1/\sigma = 0.9$,
$b_1/\sigma = b_2/\sigma = 1.0$.

@@

\fig{fig:gmvrtoy}'s central bottom panel displays the distribution of fractional residuals, and demonstrates their approximately flat distribution. A gaussian fit to the fractional residuals is displayed only for optical comparison.

@@

We find that the direct sample residuals are $99.46\%$ correlated with the input noise.

@@

@@

\begin{figure*}

@@

  \includegraphics[width=\textwidth]{fig/issue3_summary.pdf}

@@

	\caption{ Standard summary plot for \gmvr. }
  \label{fig:gmvrtoy}
\end{figure*}

>>>>

Under this perspective we will consider test data generated with the parameters listed in \tbl{tb:gmvrtoy}'s left two panels.

@@

\fig{fig:gmvrtoy}'s central bottom panel displays the distribution of fractional residuals, and demonstrates their approximately flat distribution. A gaussian fit to the fractional residuals is displayed only for comparison. In particular, a biased fit will often have residuals that are approximately gaussian; we see that this is not the case here, and that the uniformly random noise distribution is approximately recovered.

@@

When considering many noise realizations, we find that sample noise and residuals have a typically correlation of $99.46\%$.

@@

\tbl{tb:gmvrtoy} demonstrates \gmvr{}'s accurate recovery of the underlying model parameters. We note that that in going from \gmvr{}'s initial output contains terms in the numerator which correspond to the addition of a constant to the overall model, thus correcting for the difference between the offset parameter, $\mu$, and the true, but arbitrary, mean of the dataset.

@@

@@

% $\mu = 50.0$,
% %
% $a_0 = 1.1$,
% %
% $a_1 = 0.2$,
% %
% $a_2 = 0.5$,
% %
% $a_3 = 1.0$,
% %
% $1/\sigma = 0.9$,
% %
% $b_1/\sigma = b_2/\sigma = 1.0$.

@@

\begin{table}
  \caption{Summary of recovered model parameters for \gmvr{} toy problem.}
  \label{tb:gmvrtoy}
  \begin{tabular}{|c|c|c|c|}
    \hline
    \hline
    Parameter & Training Value & Modeled Value & Difference \\ \hline \hline
    $\mu$ & 50.0 & 49.9915 & 0.0171 \% \\ \hline
    $a_0$ & 1.1 & 1.1374 & 3.4002 \% \\ \hline
    $a_1$ & 0.2 & 0.2000 & 0.0000 \% \\ \hline
    $a_2$ & 0.5 & 0.5068 & 1.36784 \% \\ \hline
    $a_3$ & 1.0 & 1.0063 & 0.6300 \% \\ \hline
    $1/\sigma$ & 0.9 & 0.9375 & 4.1612 \% \\ \hline
    $b_1/\sigma$ & 1.0 & 0.9941 & 0.5906 \% \\ \hline
    $b_2/\sigma$ & 1.0 & 1.0000 & 0.0000 \% \\ \hline
    \hline
  \end{tabular}

\end{table}
%
%
\par Here, it is clear that \gmvr{} correctly recovers the functional form of the input data. In general, \gmvr{} and related techniques will attempt to model minor correlations and offsets within the training data's noise.
%
However, we have demonstrated the utility of \gmvr{} in a relatively ideal usage case where the underlying function is rational, and the training data is inly weakly contaminated with noise.
%
In the following sections, we consider cases where the functional form of the sample data is not known to be explicitly rational, but the amount of noise within the training data is negligible.
%
%
\begin{figure*}
  %
  \includegraphics[width=\textwidth]{fig/issue3_summary.pdf}
  %
	\caption{ Standard summary plot for \gmvr. }
  %
  \label{fig:gmvrtoy}
  %
\end{figure*}
